Sample-efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-01 paper/main.tex
Fig. 1 start

@@

  % Draw arrows
  \draw[arr] (i0) -- (e0);
  \draw[arr] (i1) -- (e1);
  \draw[arr] (i2) -- (e2);
  \draw[arr] (z0) -- (z1);
  \draw[arr] (z1) -- (z2);
  \draw[arr] (e0) -- (z0);
  \draw[arr] (e1) -- (zh1);
  \draw[arr] (e2) -- (zh2);
  \draw[arr] (a0) -- (z1);
  \draw[arr] (a1) -- (z2);
  \draw[darr] (zh1) -- (z1);
  \draw[darr] (zh2) -- (z2);

\end{tikzpicture}
\caption{Self-predictice loss}
\label{diagram-self-predictive}
\vskip -0.2in
\end{figure}

>>>>

% Arno's cube hack
\newcommand{\cube}{%
\resizebox{1em}{.9em}{
\begin{tikzpicture}[baseline=-1ex,cube/.style={very thick,black},
            grid/.style={very thin,gray},
            axis/.style={->,black,thick}]
 \begin{scope}[every node/.append style={yslant=-0.5},yslant=-0.5]
 [cube/.style={very thick,black},
            axis/.style={->,blue,thick}]
   \shade[right color=gray!10, left color=black!50] (0,0) rectangle +(3,3);
   \node at (0.5,2.5) {};
   \node at (1.5,2.5) {};
   \node at (2.5,2.5) {};
   \node at (0.5,1.5) {};
   \node at (1.5,1.5) {};
   \node at (2.5,1.5) {};
   \node at (0.5,0.5) {};
   \node at (1.5,0.5) {};
   \node at (2.5,0.5) {};
   \draw (0,0) grid (3,3);
 \end{scope}

 \begin{scope}[every node/.append style={yslant=0.5},yslant=0.5]
   \shade[right color=gray!70,left color=gray!10] (3,-3) rectangle +(3,3);
   \node at (3.5,-0.5) {};
   \node at (4.5,-0.5) {};
   \node at (5.5,-0.5) {};
   \node at (3.5,-1.5) {};
   \node at (4.5,-1.5) {};
   \node at (5.5,-1.5) {};
   \node at (3.5,-2.5) {};
   \node at (4.5,-2.5) {};
   \node at (5.5,-2.5) {};
   \draw (3,-3) grid (6,0);
 \end{scope}

 \begin{scope}[every node/.append style={
     yslant=0.5,xslant=-1},yslant=0.5,xslant=-1
   ]
   \shade[bottom color=gray!10, top color=black!80] (6,3) rectangle +(-3,-3);
   \node at (3.5,2.5) {};
   \node at (3.5,1.5) {};
   \node at (3.5,0.5) {};
   \node at (4.5,2.5) {};
   \node at (4.5,1.5) {};
   \node at (4.5,0.5) {};
   \node at (5.5,2.5) {};
   \node at (5.5,1.5) {};
   \node at (5.5,0.5) {};
   \draw (3,0) grid (6,3);  
 \end{scope}
\end{tikzpicture}}}

@@

  % Draw arrows
  \draw[arr] (i0) -- (e0);
  \draw[arr] (i1) -- (e1);
  \draw[arr] (i2) -- (e2);
  \draw[arr] (z0) -- node[below,font=\tiny] {Dynamics} (z1);
  \draw[arr] (z1) -- node[below,font=\tiny] {Dynamics} (z2);
  \draw[arr] (e0) -- node[above,font=\tiny,rotate=90,yshift=6pt] {Normalization} (z0);
  \draw[arr] (e1) -- (zh1);
  \draw[arr] (e2) -- (zh2);
  \draw[arr] (a0) -- (z1);
  \draw[arr] (a1) -- (z2);
  \draw[darr] (zh1) -- (z1);
  \draw[darr] (zh2) -- (z2);

  % Add normalization
  \node[circle,fill=white,inner sep=0] at ($(e0)!.5!(z0)$) {\cube};
  \node[circle,fill=white,inner sep=0] at ($(e1)!.5!(zh1)$) {\cube};  
  \node[circle,fill=white,inner sep=0] at ($(e2)!.5!(zh2)$) {\cube};

\end{tikzpicture}
\caption{Self-predictice loss We denote our normalization scheme by \cube.}
\label{diagram-self-predictive}
\vskip -0.2in
\end{figure}
